Modular Model-Checking of a Byzantine Fault-Tolerant Protocol

### 2017-02-27 paper/paper.tex
reviewers: added a little more detail in the intro about the model.

\begin{abstract}
With proof techniques like IC3 and $k$-induction, model-checking
scales further than ever before.  Still, fault-tolerant distributed
systems are particularly challenging to model-check given their
large state spaces and non-determinism. The typical approach to
controlling complexity is to construct ad-hoc abstractions of faults,
message-passing, and behaviors.  However, these abstractions come
at the price of divorcing the model from its implementation and
making refactoring difficult. In this work, we present a model
for fault-tolerant distributed system verification that combines
ideas from the literature including calendar automata, symbolic
fault injection, and abstract transition systems, and then we apply
the model to model-checking various implementations of the
Hybrid Oral Messages algorithm that differ in the fault model,
timing model, and local node behavior. We show that despite being
implementation-level models, the verifications are scalable and
modular, insofar as isolated changes to an implementation require
isolated changes to the model and proofs.  This work is carried out
in SAL model-checker.
\end{abstract}

@@

In this paper, we present a fault-tolerant distributed systems model, and use that model to verify several variant implementations of the Byzantine fault-tolerant Hybrid Oral Messages algorithm (\OMH)~\cite{Lincoln-Rushby}. The model combines ideas from the literature and folklore to build scalable and modular formal models suitable for infinite-state model-checking, and it reduces the need for ad-hoc abstractions and optimizations. In Section~\ref{sec:model}, we present the important aspects of the model, including calendar automata, originally developed by Dutertre and Sorea~\cite{cal}, symbolic fault-injection, and abstract transition systems for verification.

@@

>>>>

\begin{abstract}
With proof techniques like IC3 and $k$-induction, model-checking scales further
than ever before. Still, fault-tolerant distributed systems are particularly
challenging to model-check given their large state spaces and
non-determinism. The typical approach to controlling complexity is to construct
ad-hoc abstractions of faults, message-passing, and behaviors. However, these
abstractions come at the price of divorcing the model from its implementation
and making refactoring difficult. In this work, we present a model for
fault-tolerant distributed system verification that combines ideas from the
literature including calendar automata, symbolic fault injection, and abstract
transition systems, and then use it to model-checking various implementations of
the Hybrid Oral Messages algorithm that differ in the fault model, timing model,
and local node behavior. We show that despite being implementation-level models,
the verifications are scalable and modular, insofar as isolated changes to an
implementation require isolated changes to the model and proofs. This work is
carried out in SAL model-checker.
\end{abstract}

@@

In this paper, we present a fault-tolerant distributed systems model, and use that model to verify several variant implementations of the Byzantine fault-tolerant Hybrid Oral Messages algorithm (\OMH)~\cite{Lincoln-Rushby}. The model combines various ideas from the literature and individual verification efforts to build scalable and modular formal models suitable for infinite-state model-checking, and it reduces the need for ad-hoc abstractions and optimizations. In Section~\ref{sec:model}, we present the important aspects of the model, including calendar automata, originally developed by Dutertre and Sorea~\cite{cal}, symbolic fault-injection, and abstract transition systems for verification.

@@

Our primary contributions are (1) a model-checking verification of an $\OMH$ implementation, and (2) demonstrating that our modeling paradigm allows for modular verification.
